SVG: The Paper

### 2022-08-18 Analysis/index.Rmd
Graphs for ecvp talk

#ggsave("../Figures/qjep_indiv_diff.pdf", 
#       plt_a + plt_b + 
#         plot_layout(guides = "collect") & theme(legend.position = "right"), width = 8, height = 4)
```

@@

timedat %>% data_grid(condition, time_taken_s = seq_range(time_taken_s, 5)) %>%
  add_epred_draws(m, re_formula = NA, ndraws = 100) %>%
  ggplot(aes(time_taken_s, fill = condition)) + 
  stat_lineribbon(aes(y = .epred), alpha = 0.5, .width = c(0.53, 0.97)) +
  geom_jitter(data = timedat, aes(y = acc, colour = condition), 
              alpha = 0.05, width = 0, height = 0.005, colour = "black") +
  scale_x_continuous("scaled log response time (log seconds)") + 
  scale_y_continuous("model accuracy")  + 
  scale_colour_discrete(guide = "none") +
  coord_cartesian(ylim = c(0.4, 0.9)) +
  guides(fill = guide_legend(reverse = TRUE)) +
  facet_wrap(~ condition) -> plt

@@

plt + geom_path(data  = d_pred,
                aes(y = .epred, 
                    group = interaction(condition, observer)),
                alpha = 0.25)

@@

```{r, message = FALSE, warning = FALSE, fig.cap = "The relationship between the time taken to complete a single target selection and how predictible it is."}

# 
# my_model <- brm(acc ~ time_taken:condition + (1|observer), timedat)

a %>% select(observer, condition, trial, found, selected_max) %>%
  full_join(d, by = c("observer", "condition", "trial", "found")) %>%
  arrange(observer, condition, trial, found) %>%
  mutate(
    RTd = RT - lag(RT),
    RTd = if_else(found == 1, 0, RTd)) %>%
  filter(RTd < 2, is.finite(RTd)) %>%
  mutate(
    time_bin = cut(RTd,breaks = 50, labels = FALSE)) %>%
  group_by(observer, condition, time_bin) %>%
  summarise(acc = mean(selected_max)) %>%
  ggplot(aes(time_bin, acc, group = observer)) +
  geom_path(alpha = 0.2) +
  geom_smooth(se= F, alpha = 0.1, method = lm) + 
  facet_grid(~condition)

@@

create_post_plot("x") + create_post_plot("y") + plt_mu
#ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
```

@@

plt_dat %>% filter(dim == "x") %>%
  ggplot(aes(x, z, group = interaction(c, draw), colour = c)) +
  geom_path(alpha = 0.1) + 
  facet_wrap(~dim) + 
  theme(legend.position = "none")  + 
    scale_y_continuous("likelihood") -> plt_x

plt_dat %>% filter(dim == "y") %>%
  ggplot(aes(x, z, group = interaction(c, draw), colour = c)) +
  geom_path(alpha = 0.1) + 
  facet_wrap(~dim) + 
  theme(legend.position = "none",
        axis.title.y = element_blank()) +
  scale_x_continuous("y") + 
    scale_y_continuous("likelihood") -> plt_y

gather_draws(m, lambda[observer]) %>%
  median_hdci(.value) %>%
  arrange(.value) %>%
  mutate(observer = factor(observer, levels = observer)) %>%
  ggplot(aes(observer, .value, ymin = .lower, ymax = .upper)) + 
  geom_errorbar() +
  scale_y_continuous("lambda") + 
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) -> plt_lambdas

@@

#ggsave("../Figures/init_sel2_mdl.pdf", width = 10, height = 3.5)
```

@@

dw %>% group_by(observer, method) %>%
  summarise(acc = mean(max_item == 1), .groups = "drop") %>%
  ggplot(aes(y = acc, fill = method)) + geom_boxplot(alpha = 0.5) + 
  geom_hline(yintercept = 1/40, linetype = 2) + 
  scale_y_continuous("Prop. trials first sel. correct") +
  theme(legend.position = "none") +  
  scale_fill_manual(values = col2) -> plt2

@@

#ggsave("../Figures/qjep_init_sel_preds.pdf", 
#       plt1 / (plt2 + plt3)  + plot_layout(guides = "collect"),
#       width = 10, height = 6)

>>>>

ggsave("../Figures/qjep_indiv_diff.pdf", 
       plt_a + plt_b + 
         plot_layout(guides = "collect") & theme(legend.position = "right") & 
         theme_bw(), width = 8, height = 4)
```

@@

timedat %>% data_grid(condition, time_taken_s = seq_range(time_taken_s, 5)) %>%
  add_epred_draws(m, re_formula = NA, ndraws = 100) %>%
  ggplot(aes(time_taken_s, fill = condition)) + 
  stat_lineribbon(aes(y = .epred), alpha = 0.75, .width = c(0.53, 0.97)) +
  geom_jitter(data = timedat, aes(y = acc, colour = condition), 
              alpha = 0.05, width = 0, height = 0.005, colour = "black") +
  scale_x_continuous("scaled log response time (log seconds)") + 
  scale_y_continuous("model accuracy")  + 
  scale_colour_discrete(guide = "none") +
  coord_cartesian(ylim = c(0.4, 0.9)) +
  guides(fill = guide_legend(reverse = TRUE)) +
  facet_wrap(~ condition, nrow = 2) -> plt

@@

plt + geom_path(data  = d_pred,
                aes(y = .epred, 
                    group = interaction(condition, observer)),
                alpha = 0.25) -> plt

ggsave("../Figures/trial_time.png", plt + theme_bw() + theme(legend.position = "none"), width = 4, height = 6)

@@

```{r, message = FALSE, warning = FALSE, fig.cap = "The relationship between the time taken to complete a single target selection and how predictible it is."}
breaks = c(seq(0.1, 0.8,0.1),1, 1.5, 2, 3, 4, 5, 6)

a %>% select(observer, condition, trial, found, selected_max) %>%
  full_join(d, by = c("observer", "condition", "trial", "found")) %>%
  arrange(observer, condition, trial, found) %>%
  mutate(
    RTd = RT - lag(RT),
    RTd = if_else(found == 1, 0, RTd),
    logRTd = log10(RTd)) %>%
  filter(is.finite(logRTd)) %>%
  mutate(
    time_bin = cut(logRTd,breaks = 25)) %>%
  separate(time_bin, into = c("binS", "binE"), ",") %>%
  mutate(binS = parse_number(binS),
         binE = parse_number(binE),
         logRTd = (binS + binE)/2,
         RTd = 10^logRTd) %>%
  group_by(observer, condition, RTd) %>%
  summarise(acc = mean(selected_max),
            n = n()) %>%
  filter(n > 5) %>%
  ggplot(aes(x = RTd, y = acc, colour = condition)) + 
  geom_jitter(height = 0, width = 0.02, alpha = 0.5) +
  scale_x_log10("inter-item selection time", breaks = breaks) + 
  scale_y_continuous("model accuracy") + 
  stat_smooth(method = glm, method.args = list(family = "binomial"), se = FALSE, alpha = 0.5) +
  theme_bw() + theme(legend.position = "none")

ggsave("../Figures/targ_time.png", width = 7, height = 4)

@@

create_post_plot("x") + create_post_plot("y") + plt_mu & theme_bw()
ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
```

@@

plt_dat %>% filter(dim == "x") %>%
  ggplot(aes(x, z, group = interaction(c, draw), colour = c)) +
  geom_path(alpha = 0.1) + 
  facet_wrap(~dim) + 
  theme_bw() + 
  theme(legend.position = "none")  + 
    scale_y_continuous("likelihood") -> plt_x

plt_dat %>% filter(dim == "y") %>%
  ggplot(aes(x, z, group = interaction(c, draw), colour = c)) +
  geom_path(alpha = 0.1) + 
  facet_wrap(~dim) + 
  theme_bw() + 
  theme(legend.position = "none",
        axis.title.y = element_blank()) +
  scale_x_continuous("y") + 
    scale_y_continuous("likelihood") -> plt_y

gather_draws(m, lambda[observer]) %>%
  median_hdci(.value) %>%
  arrange(.value) %>%
  mutate(observer = factor(observer, levels = observer)) %>%
  ggplot(aes(observer, .value, ymin = .lower, ymax = .upper)) + 
  geom_errorbar() +
  scale_y_continuous("lambda") + 
  theme_bw() + 
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) -> plt_lambdas

@@

ggsave("../Figures/init_sel2_mdl.pdf", width = 10, height = 3.5)
```

@@

dw %>% group_by(observer, method) %>%
  summarise(acc = mean(max_item == 1), .groups = "drop") %>%
  ggplot(aes(x = method, y = acc, fill = method)) + geom_boxplot(alpha = 0.5) + 
  geom_hline(yintercept = 1/40, linetype = 2) + 
  scale_y_continuous("Prop. trials first sel. correct") +
  theme(legend.position = "none") +  
  scale_fill_manual(values = col2) -> plt2

@@

ggsave("../Figures/qjep_init_sel_preds.pdf", 
       (plt2 / plt3) & theme_bw() & theme(legend.position = "none"),
       width = 4, height = 8)
